\LaTeXe\ guide for the Journal of Functional Programming

### 2019-04-28 papers/jfp/10-conclusions.tex
More tidying up of S8

We have investigated multiple build systems, showing how their properties are consequences of two implementation choices: what order you build in and how you decide whether to rebuild. By first decomposing the pieces, we show how to recompose the pieces to find new points in the design space. In particular, a simple recombination leads to a design for a monadic suspending cloud build system. Armed with that blueprint we hope to actually implement such a system as future work.

>>>>

We have investigated multiple build systems, showing how their properties are consequences of two implementation choices: what order you build in and how you decide whether to rebuild. By first decomposing the pieces, we show how to recompose the pieces to find new points in the design space. In particular, a simple recombination leads to a design for a monadic suspending cloud build system, which we have implemented and use in our day-to-day development.

### 2019-04-28 papers/jfp/8-engineering.tex
More tidying up of S8

\noindent
It is possible to implement \hs{selfTracking} without relying on GADTs and typed
tasks presented in~\S\ref{sec-polymorphism}, but the cost of using partial
functions.

>>>>

\noindent
It is possible to implement \hs{selfTracking} without relying on GADTs and typed
tasks presented in~\S\ref{sec-polymorphism}, at the cost of using partial
functions.

### 2019-04-28 papers/jfp/9-related.tex
Lift the contents of todo.md into the .tex and start to do the proposed splits
Work on S3
More tidying up of S8

\item \Redo~\cite{redo-idea}\cite{grosskurth2007redo}\cite{redo} almost exactly
matches \Shake at the level of detail given here, differing only on aspects like
polymorphic dependencies~\S\ref{sec-polymorphism}.

>>>>

\item \Redo~\cite{redo-idea,grosskurth2007redo,redo} almost exactly
matches \Shake at the level of detail given here, differing only on aspects like
polymorphic dependencies~\S\ref{sec-polymorphism}.
